
In semiconductor sensors a traversing charged particle creates free electron-hole pairs which drift under the influence of an electric field to the read-out electrodes. 
If all charge carriers are collected by a single strip/pixel, the position resolution depends only on the distance between strips/pixels, i.e.\ on the pitch size. 
If the size of the lateral broadening of the charge is comparable with the strip/pixel pitch size, the charge may be collected at two neighboring strips/pixels. %FIXME rephrase, it is not clear to the reader what you want to say. By comparing things they dont change their behaviour
This effect, called charge sharing, can improve the accuracy of the measurement of the incident position. 
Charge sharing can be achieved by using a magnetic field, by tilting the sensor or increasing the lateral size of the charge distribution during the drift.

The charge carriers drift along the lines of an electric field. 
In order to achieve lateral movement of the charges, the electric field has to be modified. 
To manipulate the electric field, implants deep in the bulk are used. 
p$^{\textrm{+}}$-implants in a p-bulk sensor are achieved e.g.\ by incorporation of Boron atoms and create repulsive areas for electrons. 
Usage of deep p$^{\textrm{+}}$-implants leads to the increase of the value of the doping concentration in the sensor. 
This causes to increasing of the value of the effective doping concentration N$_{\textrm{eff}}$.
A high value of N$_{\textrm{eff}}$ implies an the increased depletion voltage V$_{\textrm{depl}}$:

\begin{equation}
 N_{eff}=N_{D}-N_{A} ,
\end{equation}

\begin{equation}
 V_{depl}=\frac{q_0 D^2 |N_{eff}|}{2 \epsilon_r \epsilon_0 } ,
\end{equation}

\noindent where N$_{\textrm{D}}$ and N$_{\textrm{A}}$ are donator and acceptor concentration, D is the sensor thickness.
To control the value of N$_{\textrm{eff}}$, additional deep implants of type n$^{\textrm{+}}$ are used. 
The n$^{\textrm{+}}$ implants are placed between two p$^{\textrm{+}}$ implants \ref{fig:geo-elfield}~(A). %FIXME reference to figure 2 (A) ?! Otherwise the reader does not understand what you explain here!
A careful balancing of the the doping concentrations of p$^{\textrm{+}}$ and n$^{\textrm{+}}$ implants yields a controlled value of N$_{\textrm{eff}}$ and, correspondingly, V$_{\textrm{depl}}$. 
The number of implant layers should be as small as possible in oder to keep the production process as simple as possible. 
%FIXME have a look at the newcommand exampels in the main.tex, how to get normal script indices _{\textrm{blabla}}. e.g. N_{\textrm{D}}

